---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# myriad

## About

Myriad Pro-based themes for ggplot, `theme_myriad()` and `theme_myriad_semi()`. Various hacks / workaround functions to try to have both a systemfonts/ragg pipeline for pngs and a showtext one for pdf devices.

Note that this repo does not include the Myriad font files (the `.otf` files), which are owned by Adobe. You may already have them installed on your computer, or they may have come bundled with your copy of Acrobat Reader or other Adobe software.


## Usage

When creating PDFs, use with `showtext`. 

```{r setup, message=FALSE}
library(tidyverse)
library(ggrepel)


```

```{r, message=FALSE}
library(showtext)
showtext_opts(dpi = 300)
showtext_auto()

library(myriad)

# Semi variant
import_myriad_semi()

# Condensed for in-graph text
import_myriad_condensed()

# ggplot theme
theme_set(theme_myriad_semi())

```

# Basic Test

```{r, fig.width=6, fig.height=4}
p <- ggplot(mtcars, 
            aes(x = wt, y = mpg)) + 
  geom_point() + 
  labs(x = "Weight", y = "Miles per Gallon", 
       title = "This is the title", subtitle = "This is the subtitle", 
       caption = "This is the caption")  

p
```

# Check PDF works

```{r}
ggsave("man/figures/ggfont-test-myrnew-2.pdf", p, width = 6, height = 4)
```


# With labels

```{r, fig.width=8, fig.height=4}
out <- mtcars |>
  mutate(car = rownames(mtcars)) |> 
  as_tibble() |> 
  ggplot(aes(x = wt, y = mpg, label = car)) + 
  geom_text_repel(family = "Myriad Pro Condensed") +
  facet_wrap(~ cyl) + 
  labs(title = "Title", 
       subtitle = "Subtitle")

out
```


## Check PDF works

```{r}
ggsave("man/figures/ggfont-test-myrnew-3.pdf", out, width = 12, height = 8)
```


